Graph bipartitioning and you

### 2016-01-17 evolutionaryComputation/2-practical/report.tex
this has a sane plot thing that works

\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsRule{*}{mps}{*}{}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{emp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{svg}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

@@

Use original file by doing a substr(30)
\end{document}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsRule{*}{mps}{*}{}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{emp}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{svg}
\usepackage{pgfplots}
\usepackage{pgfplotstable}

\pgfplotsset{
    compat=1.9,
    compat/bar nodes=1.8
}

\begin{filecontents*}{dataTable.txt}
zero 	name 		firsty 		secondy		errbotstart		errbotend 		errtopstart			errtopend
0 		MLS           0         	1			0.1				0.2				0.1	               0.2
0 		ILS           1         	2			0.3				0.1             1.5               0.4
0 		GLS           2         	3.5			0.5				0.2             0.3               0.4
\end{filecontents*}

\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

@@

\pgfplotstableread{dataTable.txt}\dataTable
\begin{tikzpicture}
\pgfplotsset{set layers}
\begin{axis}[
	ybar stacked,
	xlabel={Algorithm},
	xticklabels from table={dataTable.txt}{name},
	xtick=data,
	ylabel={Time}
]

% Layers needed to get error bars on top of lower blue rectangle
\addplot[color=white]
table[on layer=axis grid, x expr=\coordindex, y=firsty]{\dataTable};

\addplot[color=red] plot[on layer=axis lines,error bars/.cd, y dir=both, y explicit] 
table[x expr=\coordindex, y=zero, y error minus=errbotstart, y error plus=errbotend]{\dataTable};

\addplot[color=red] plot[on layer=axis lines,error bars/.cd, y dir=both, y explicit] 
table[x expr=\coordindex, y=secondy, y error minus=errtopstart, y error plus=errtopend]{\dataTable};

\end{axis}

\end{tikzpicture}

\end{empfile}
\end{document}
